What's in a name? On the automated topic naming of software maintenance activities

### 2010-03-06 icpc/icpc2010.tex
spellcheck

Topics arise from the wide variety of issues which occur during a software project's lifecycle. These topics can relate to, among others, the problem domain, the processes and tools used, or the development artifacts themselves.  The set of development topics for a given project can sometimes be extracted automatically by analyzing artifacts within software repositories, such as change-log comments that developers create when committing revisions to the project's source control system.  Our previous work dealt with topic trends, which are topics that recur over time~\cite{Hindle09ICSM}. We observed that topic trends were often non-functional requirements.

@@

We took our annotated dataset and applied supervised learners to it. Because our dataset was of word counts we expected Bayesian techniques, often used in spam filtering, to perform well. We also tried other learners that WEKA~\cite{weka09} provides: rule learners, tree learners, vector space learners, and support vector machines.  Table \ref{tab:best-learn-per-tag} shows the performance of the best performing learner per label.  We considered the best learner for a label to be the one which had the highest ROC value for that label. Table \ref{tab:best-learn-per-tag} shows the ROC value, the accuracy of a ZeroR learner ( a learner which just chooses the largest category all of the time), the difference in accuracy between the best learner and ZeroR, and the F-measure for that particular learner. The ZeroR difference is often negative, but in particular for labels which are not as common this can be expected because any miscategorization will hurt accuracy, this is why the F1 (F-measure) and the ROC values are useful as they can better present performance on labels which are not applicable to the majority of samples.

@@

We have presented the results of Mulan's multi-label learners in Table \ref{tab:mulan}.  Binary Relevance (BR), Calibrated Label Ranking (CLR) and Hierarchy Of Multilabel classifiERs (HOMER), performed the best. HOMER and BR acts as a hierarchy of learners, BR is flat while HOMER tries to build a deeper hierarchy in order to build a more accurate learner~\cite{mulan}. We feel that these classifiers performed better than other multilabel classifiers because they have the best micro and macro ROC scores than the other classifiers although their results seem comparable to the naive Bayesian learners we used in Section \ref{sec:suplabelling}.

>>>>

Topics arise from the wide variety of issues which occur during a software project's life-cycle. These topics can relate to, among others, the problem domain, the processes and tools used, or the development artifacts themselves.  The set of development topics for a given project can sometimes be extracted automatically by analyzing artifacts within software repositories, such as change-log comments that developers create when committing revisions to the project's source control system.  Our previous work dealt with topic trends, which are topics that recur over time~\cite{Hindle09ICSM}. We observed that topic trends were often non-functional requirements.

@@

We took our annotated data-set and applied supervised learners to it. Because our data-set was of word counts we expected Bayesian techniques, often used in spam filtering, to perform well. We also tried other learners that WEKA~\cite{weka09} provides: rule learners, tree learners, vector space learners, and support vector machines.  Table \ref{tab:best-learn-per-tag} shows the performance of the best performing learner per label.  We considered the best learner for a label to be the one which had the highest ROC value for that label. Table \ref{tab:best-learn-per-tag} shows the ROC value, the accuracy of a ZeroR learner ( a learner which just chooses the largest category all of the time), the difference in accuracy between the best learner and ZeroR, and the F-measure for that particular learner. The ZeroR difference is often negative, but in particular for labels which are not as common this can be expected because any miscategorization will hurt accuracy, this is why the F1 (F-measure) and the ROC values are useful as they can better present performance on labels which are not applicable to the majority of samples.

@@

We have presented the results of Mulan's multi-label learners in Table \ref{tab:mulan}.  Binary Relevance (BR), Calibrated Label Ranking (CLR) and Hierarchy Of Multi-label classifiERs (HOMER), performed the best. HOMER and BR acts as a hierarchy of learners, BR is flat while HOMER tries to build a deeper hierarchy in order to build a more accurate learner~\cite{mulan}. We feel that these classifiers performed better than other multi-label classifiers because they have the best micro and macro ROC scores than the other classifiers although their results seem comparable to the naive Bayesian learners we used in Section \ref{sec:suplabelling}.
